Designing a high-performance boundary element library with OpenCL and Numba

### 2021-04-14 opencl.tex
add colouring diagram

>>>>

\begin{figure}
	\center
	\input{img/colouring}
	\caption{The triangles in this mesh have been colored (using a greedy algorithm) so that no two neighbouring triangles are the same color. Sets of triangles of the same color can therefore be processed together as they are guaranteed to not be neighbors. [The dots on each cell are included as a visual aid for anyone who prints this article in black and white.]}
	\label{fig:colouring}
\end{figure}
